Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations

### 2016-03-18 paper.tex
.

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\section{Robot Grasping in Clutter}
We now describe the grasping in clutter problem, the supervisor hierarchy that we used to solve it and our deep learning policy architecture.

\subsection{Grasping in Clutter}\label{sec:task}
\mlnote{Should we just merge this with the original, problem objective?}
Consider a robot in an shipping warehouse. The robot has an intended goal object for it to grasp on a shelf, however other objects could obstruct the path towards the goal object. In the shipping warehouse, setting these objects are most likely unknown to the robot and it would not have a stored model of their mass and friction properties. These obstructions of unknown  movable objects prevent leveraging  control techniques, because the robot does not posses a dynamics model of how the objects behave under different contact forces. ~\cite{kitaevphysics,kingnonprehensile}.

Instead of purely using analytical planning techniques, the robot could learn from past experiences how to reach a goal object surrounded by a set of training objects. Then the robot applies that manipulation policy to a set of  visually similar objects.

We are thus interested in teaching a robot, $\pi_\theta$ on a state space $\mathcal{X}$, which is image data of  K collision objects and goal object in a bounded workspace.  The underlying reward function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, is the binary evaluation of successfully grasping the goal object. This reward function can be too delayed to optimize directly. Thus, we leverage a hierarchy of supervisors and Online LfD (described previously) to minimize the expected surrogate loss between the robot's policy $\pi_\theta$ and the most skilled supervisor's, $\tilde{\pi}_M$.

\subsection{Supervisor Hierarchy}\label{sec:hier}
In this section, we list each supervisor in the order they appear in our hierarchy. The first supervisor is deemed the least expensive.

\noindent \textbf{Motion Planning that Ignores Obstacles Supervisor} Our first supervisor, $S_1$, is a a motion planner that that computes the trajectory the robot should move in to reach the goal object, or yellow circle, by ignoring obstacles.  Thus we refer to $S_1$ as Motion Planning that Ignores Obstacle (MPIO) supervisor. Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control. The template matching is implemented in OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}.

In this stage, the MPIO supervisors only tries to teach the robot to move towards the goal. Note that the MPIO supervisor's examples does not have any knowledge about how the cluttered objects will respond to the forces applied via the robot arm, which results in sub-optimal polices. However, the MPIO supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples. Thus, the cost of the MPIO supervisor is $C_1 = 0.01$.

\begin{figure}[t]
\centering

@@

\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that can perform  provide examples for  \$0.12 per robot trial. Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a  higher cost, $C_2 = 0.1$.

In order to get examples from a CrowdSourced Supervisor, we designed an interface shown in Fig. \ref{fig:overlays}. The interface draws a transparent overlay that shows how the robot would respond provided the current control Thus, allowing for the AMT worker to see the magnitude and effect their example would have on the robot.

We additionally designed a tutorial for the CrowdSourced Supervisor. We first desribe the learning task to them as a robot that is trying to reach a yellow cynlider and needs their help learning how to get it. Then we have them perform designated motions with a virtual robot, which helps them understand how the robot's dynamics behave. We additionally provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the CrowdSourced Supervisor to only label when they are sure in their decision, in order to prevent contradictory examples associated with them second guessing themselves.

To help ensure quality, we give all CrowdSourced Supervisor the same robot trial first and measure their examples against the examples form a  Human Expert Supervisor. If the average Squared-Euclidean distance between examples is above a threshold of the Human Expert's examples or the number of examples they provided is above a threshold of the number the Human Expert provided, the Crowdsource Supervisor is not asked to provide additional examples.

\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in machine learning and robotics, which costs $C_3=1.0$. The Human Expert Supervisor uses the same interface , shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

An expert supervisor can be used in a variety of scenarios.They first would have a better intuition of the physical limitations of the robot and environment, such as joint limits or how certain objects might behave under force. Furthermore, they would also understand how the examples given could lead to better training of the robot's policy $\pi_\theta$. For example, understanding the feature space the policy lies in can lead the Human Expert to not providing contradictory examples.

\subsection{Neural Network Policy Architecture}
Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}. Our network architecture consists of 1 convolutional layer with 5 channels and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a four dimensional control signal. We used ReLus to separate the different layers and a final tanh on the output to scale the output between -1 and 1.

The control examples was scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.  We then validated that all information (i.e. location of the gripper, cluttered shapes and goal object) where still visible in the masked image.

To determine our architecture we preformed a grid search over different architectures  trained after 400 iterations with a batch size of 200. The set of architectures consist of different network architectures as well as different momentum terms, and weight initialization schemes. We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.

@@

In this section, we first describe the grasping in clutter experimental setup. Then we test how the supervisor hierarchy performs versus not leveraging a hierarchy. We then test how high of Quality the CrowdSource supervisor is. Then, we experiment with different ways to advance in the hierarchy. Finally, we look at using all three supervisors and to train a robot for the grasping in clutter task.

\subsection{Experimental Setup}
For experimenting in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

The objects in clutter are made of Medium Density Fiberboard and each one is on average 4" in diameter. The objects deemed cluttered are painted Red and the goal object is painted yellow. There is an inscribed circle around the work space to keep the robot from pushing the objects outside of the work space. The inscribed circle can make the task more challenging because the robot cannot simply "sweep" the cluttered objects off the table.

The robot, shown in Fig. \ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper. The robot is commanded via state position requests, which are tracked by a tuned PID controller. We used relative state control because 1) it is easier to enforce stay out zones (such as where a human operator might be)  and 2) registering state control to a labeling interface in Fig. \ref{fig:overlays} is more straightforward than motor commands.   The policy $\pi_\theta$ outputs delta positions that are bounded by $15^\circ$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step. There is $T=100$ time steps in a trajectory.

To test the performance of a policy, we created a test set composed of 20 different configurations each containing objects that were not trained on.  The test set configurations varied in number of objects on the table, size of objects and relative pose of each object. The objects that were trained on and those that were only tested on can be seen in Fig. \ref{fig:shape_set}.  We measure success as defined by three situations: Not Contact, Contact and Grasped. Examples of the robot in these situations can be seen in Fig. \ref{fig:suc_meas}.

The Not Contact situation corresponds to the case when the robot's gripper is not touching the goal object at the end of a rollout. Examples of when this happens is when the robot fails to push the objects away or does not head in the direction of the yellow circle. The Contact situation is defined as the robot touches the goal object with its gripper, but it is not enclosed in the gripper. Examples of when this happens is when the robot gets a small obstacle object trapped in the gripper first, or when the root slightly misses the yellow circle on its approach. Grapsed is defined as getting the goal object inside the gripper at the end of a trajectory. We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.

In all experiments we used a batch size of 20 trials per iterations or 2000 images, thus 100 trials corresponds to 5 iterations.

@@

\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert. The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).  (WILL CLEAN UP ONCE WE DESCRIBE SCORE)  }

@@

We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .  We compare having only a MPIO Supervisor for a fixed amount of data to having only an Human Expert, and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

@@

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained with the MPIO to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.18) }
\label{fig:cost_result}
\end{figure}

\subsection{Quality of Crowdsourced Supervisor}
We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an experiment using the AMT platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the crowdsourced supervisor achieves a score of $0.41\%$. The policy trained with the hierarchical crowdsourced and MPIO supervisor receives $0.43\%$ on our test set compared to $0.55\%$ with the motion planning and expert supervisors hierarchy. The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.

@@

\subsection{Advancing in the Hierarchy}
We further test how to advance between supervisors in the hierarchy.We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$. Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

We compare each strategy on a hierarchy of a MPIO supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.  Our results reported in Fig.\ref{fig:cost_result} , show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$. Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.

An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward. This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.

We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically in Sec. \ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

\subsection{Scaling the Hierarchy}
The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: MPIO, crowdsourced and human expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply. Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.

@@

\section{Discussions and Future Work}
For highly stochastic domains like grasping in clutter, using a hierarchy of supervisors to bootstrap performance at a lower cost is an interesting avenue of research. Our results suggest that we can scale up the amount of data needed to learn the task at a much lower cost than only querying the most-skilled supervisor. However, much work still needs to be done in determining how to appropriately select the next supervisor to receive examples from. While our current strategy worked well empirically, it remains to be seen if this would apply to other domains.

>>>>

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\section{Robot Grasping in Clutter}
Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
planar objects obstruct the path towards the goal object. Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledte of explicit object or dynamics models and instead learn a grasping policy directly from labelled
overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.

\noindent \textbf{Algorithmic Supervisor (AS)} Our first supervisor, $S_1$, is a first order motion planner that that computes
control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
computes the relative change in direction the robot should apply as a control. The template matching is implemented in
OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
We assign a cost of $C_1 = \$0.01$ to this supervisor.
\begin{figure}[t]
\centering

@@

\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
supervision examples for approximately \$0.1 per robot trial. 
We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree to
the current roll-out.

We additionally designed a tutorial for the CrowdSourced Supervisor. We first desribe the learning task to them as a
robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the CrowdSourced
Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
with random guesses.

To help ensure quality, we provide all CrowdSourced Supervisors with the same robot trial first and measure their
performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.

\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in
machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
interface as the CrowdSourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.

An expert supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
joint limits and experience in how certain objects might behave under force. Furthermore, the expert supervisor might
have an intuition for how training examples could lead to better training of the robot's policy $\pi_\theta$.

@@

We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
with one supervisor. We then evaluate the quality the CrowdSource supervisors.

\subsection{Experimental Setup}
We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper. The robot is commanded via state position requests, which are tracked by a tuned PID controller. We used
relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
be) to register state controlsignals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
painted Red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
the workspace, and thus adding to the difficulty of the task challenging.

Our policy $\pi_{\theta}$ is represented as a deep neural network, which was trained using
TensorFlow~\cite{tensorflow2015-whitepaper}. Our network architecture consists of 1 convolutional layer with 5 channels
and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a
four dimensional control signal. We used ReLus to separate the different layers and a final tanh on the output to scale
the output between -1 and 1. Each policy runs for a total of $T=100$ timesteps.

The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.  We then validated that all information (i.e. location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
As a result, we labelled to set these output degrees of freedom with zero and instead automatically closed the gripper
at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
extension degree of freedom.

To determine our network architecture we preformed a search over {\color{blue} FP: how many?} different architectures trained after 400 iterations with a batch size of 200. The set of architectures consist of different network architectures as well as different momentum
terms { \color{blue} FP: what? details}, and weight initialization schemes. We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.

To test the performance of a policy, we created a test set composed of 20 different configurations each containing
objects that were not in the training set.  The test set configurations varied in the number of objects on the table
{\color{blue} FP: how many?}, size of objects and relative pose of each object. The training objects and the novel
objects introduced during testing are shown in Fig. \ref{fig:shape_set}.  We measure success by weather the object was
in the gripper at the final timestep. Examples are displayed in Fig. \ref{fig:suc_meas}. 
Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images.
Thus 100 robotic trials correspond to 5 iterations of DAgger.

@@

\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs
shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies
only trained with one supervisor: AS, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a
hierarchy of supervisors: AS and Crowdsource, AS and Human Expert, AS, Crowdsourced and Human Expert. The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).  (WILL CLEAN UP ONCE WE DESCRIBE SCORE)  }

@@

We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain
similar performance . We compare having only a AS Supervisor for a fixed amount of data to having only an Human Expert,
and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
first receives  100 demonstrations from the AS supervisor and  60 demonstrations from the expert supervisor.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the AS supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

@@

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
with the AS to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.18) }
\label{fig:cost_result}
\end{figure}

\subsection{Quality of Crowdsourced Supervisor}
We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an
experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor
performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations  from the algorithmic supervisor , then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.

Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
a score of $41\%$. The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $43\%$ on our test set compared to $55\%$ with the motion planning and expert supervisors hierarchy. The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.

@@

\subsection{Advancing in the Hierarchy}
We further test how to advance between supervisors in the hierarchy. We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$. Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.  Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$. Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.

An issue arises though when performing these iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward. This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.

We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the
current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the
hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
$\tilde{\epsilon}$ {\color{blue}FP:what epsilon?}. Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.

\subsection{Scaling the Hierarchy}
The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: AS, crowdsourced and human
expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply. Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.

@@

\subsection{Discussion of Failure Modes}
{\color{blue} FP: Michael, please add a 3x3 figure of "hard" examples and discuss failure modes.}

\section{Discussions and Future Work}
Our results suggest learning to grasp in clutter can more cost-efficiently be learned by employing a hierarchy of
supervisors. In future work, we intend to investigate algorithmic approaches to determining how to appropriately select
the next supervisor in a hierarchy automatically. While our current strategy worked well empirically, it remains to be 
investigated how this approach can be utilized in different application domains.
